Description of a Deterministic Unit Commitment Model with Probabilistic Reserve constraints and Network Representation

### 2022-05-06 papers/main.tex
Errors in network redispatch formulation

\begin{align}
    \sum_{g \in G_n} r^{L^+}_{glt} + rs_{nlt} = d^{L^+}_{nlt} + rinj^{L^+}_{nlt} & \quad n \in N, \; l \in L^+, \; t \in T \\
    \sum_{g \in G_n} r^{L^-}_{glt} + rc_{nlt} = d^{L^-}_{nlt} + rinj^{L^-}_{nlt} & \quad n \in N, \; l \in L^-, \; t \in T \\
    rf^{L^+}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^+}_{nlt}             & \quad b \in B, \; l \in L^+, \; t \in T \\
    rf^{L^-}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^-}_{nlt}             & \quad b \in B, \; l \in L^-, \; t \in T \\
    -F_{b} \leq f_{bt} + rf^{L^+}_{blt} \leq F_b                                 & \quad b \in B, \; l \in L^+, \; t \in T \\
    -F_{b} \leq f_{bt} + rf^{L^-}_{blt} \leq F_b                                 & \quad b \in B, \; l \in L^-, \; t \in T \\
    \sum_{n \in N} rinj^{L^+}_{nt} = 0                                           & \quad l \in L^+, \; n \in N, \; t \in T \\
    \sum_{n \in N} rinj^{L^-}_{nt} = 0                                           & \quad l \in L^-, \; n \in N, \; t \in T
\end{align}

>>>>

\begin{align}
    \sum_{g \in G_n, l'=1:l} (r^{L^+}_{glt} + rs_{nlt}) = d^{L^+}_{nlt} + rinj^{L^+}_{nlt} & \quad n \in N, \; l \in L^+, \; t \in T \\
    - \sum_{g \in G_n, l'=1:l} (r^{L^-}_{glt} + rc_{nlt}) = d^{L^-}_{nlt} + rinj^{L^-}_{nlt} & \quad n \in N, \; l \in L^-, \; t \in T \\
    \sum_{n \in N} d^{L^+}_{nlt} = \sum_{l'=1:l} D^{L^+}_{l't}                             & \quad l \in L^+, \; t \in T             \\
    \sum_{n \in N} d^{L^-}_{nlt} = -\sum_{l'=1:l} D^{L^-}_{l't}                            & \quad l \in L^-, \; t \in T             \\
    rf^{L^+}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^+}_{nlt}                       & \quad b \in B, \; l \in L^+, \; t \in T \\
    rf^{L^-}_{blt} = \sum_{n \in N} PTDF_{nb} \cdot rinj^{L^-}_{nlt}                       & \quad b \in B, \; l \in L^-, \; t \in T \\
    -F_{b} \leq f_{bt} + rf^{L^+}_{blt} \leq F_b                                           & \quad b \in B, \; l \in L^+, \; t \in T \\
    -F_{b} \leq f_{bt} + rf^{L^-}_{blt} \leq F_b                                           & \quad b \in B, \; l \in L^-, \; t \in T \\
    \sum_{n \in N} rinj^{L^+}_{nt} = 0                                                     & \quad l \in L^+, \; n \in N, \; t \in T \\
    \sum_{n \in N} rinj^{L^-}_{nt} = 0                                                     & \quad l \in L^-, \; n \in N, \; t \in T
\end{align}
